SimBio: a flexible and extensible Python package for systems modelling

### 2023-11-10 article.qmd
Include "error-prone" into first paragraph

Chemical Reaction Networks (CRN)
are the basis of many models used across the biological sciences and epidemiology.
They consist of a set of species and reactions that mediate conversions between them.
Several modalities exist to simulate these systems:
deterministic Ordinary Differential Equations (ODE) which model a macroscopic behavior,
Stochastic Differential Equations (SDE) which model microscopic fluctuations,
and jump processes (Gillespie-like simulations) which take into account the discreteness of the populations.
Hence, it is useful to write these models in a higher level description
which can be reused for these different types of simulations.
equations directly is error-prone and not easily reusable

>>>>

Chemical Reaction Networks (CRN)
are the basis of many models used across the biological sciences and epidemiology.
They consist of a set of species and reactions that mediate conversions between them.
Several modalities exist to simulate these systems:
deterministic Ordinary Differential Equations (ODE) to model a macroscopic behavior,
Stochastic Differential Equations (SDE) to model microscopic fluctuations,
and jump processes (Gillespie-like simulations) to take into account the discreteness of the populations.
Instead of writing the equations directly for each of these formulations
which is error-prone and hard to reuse,
these models can be written in a higher level description
which can be compiled for these different types of simulations.
